Analysis methods for characterizing the climate sensitivity of annual growth and woody productivity using tree-rings

### 2020-03-18 methods/analysis_methods.Rmd
minor updates

1.2. Use the [climwin](https://cran.r-project.org/web/packages/climwin/index.html) R package [(van de Pol et. al. 2016)](https://besjournals.onlinelibrary.wiley.com/doi/full/10.1111/2041-210X.12590), to identify the time window over which each candidate climate variable most strongly influences tree growth *for all species combined*. Specifically, we put the put residuals in *climwin* with with mixed effects model: `ln[residual] ~ [climate] + species + treeID (random effect)`. Outputs are saved [here](https://github.com/EcoClimLab/ForestGEO-climate-sensitivity/blob/master/results/ALL_species_mixed_model_on_residuals/). Example output is shown in Fig. 1.

@@

2.2. For each species independently, run GAM models including every combination of climate variable, DBH, and splines on year fit to each individual.
`ln[response variable] ~ DBH + [climate variables] + year (spline) + tag (random effect)`

2.3. Across all potential models, sum variable weights to determine which drivers are most important. Count the model containing those variables as the top model (even if it's not top in terms of AIC)

>>>>

1.2. Use the [climwin](https://cran.r-project.org/web/packages/climwin/index.html) R package [(van de Pol et. al. 2016)](https://besjournals.onlinelibrary.wiley.com/doi/full/10.1111/2041-210X.12590), to identify the time window over which each candidate climate variable most strongly influences tree growth *for all species combined*. Specifically, we put the residuals in *climwin* with a mixed effects model using species and tree identity as random effect: `ln[residual] ~ [climate] +  + (1 | sp) + (1 | treeID)`. Outputs are saved [here](https://github.com/EcoClimLab/ForestGEO-climate-sensitivity/blob/master/results/ALL_species_mixed_model_on_residuals/). Example output is shown in Fig. 1.

@@

2.2. For each species independently, run GAM models including every combination of climate variables (as a 2-degree polynomial to allow quadratic curve), spline of DBH (3 knots), and splines of year fit to each individual as a random effect.
`ln[response variable] ~ spline(DBH) + quad([climate variables]) + spline(year, with treeID as random effect)`

2.3. Across all possible models, sum variable AICc weights to determine which drivers are most important. Consider the model containing those variables as the top model (even if it's not top in terms of AIC)
